\Large Analyzing the Supreme Court Citation Network

### 2017-11-22 Tex/paper.tex
Inferential Results

\begin{table}[]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -5.364                                                 & -5.411                                                     & -4.155                                                     \\ \hline
Instar(2)               & 0.031                                                   & 0.025                                                      & 0.037                                                      \\ \hline
Outstar(2)              & 0.016                                                   & -0.004                                                      & 0.017                                                      \\ \hline
Mutual                  & 4.472                                                   & 3.821                                                 & 5.069                                                      \\ \hline
Triangle                & 1.275                                                   & 1.194                                                      & 1.401                                                      \\ \hline
MQ Score                & 0.174                                                   & 0.082                                                      & 0.244                                                      \\ \hline
Same Issue Area         & 1.113                                                   & 0.972                                                      & 1.152                                                      \\ \hline
Year Difference         & -0.092                                                   & -0.114                                                     & -0.085                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the timep period when Fred M. Vinson was chief justice.}
\label{bootMPLE_vinson}
\end{table}

\begin{table}[]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -3.571                                                 & -3.597                                                     & -3.460                                                     \\ \hline
Instar(2)               & 0.014                                                   & 0.013                                                      & 0.016                                                      \\ \hline
Outstar(2)              & 0.001                                                   & -0.001                                                      & 0.004                                                      \\ \hline
Mutual                  & 9.678                                                   & 8.308                                                 & 11.261                                                      \\ \hline
Triangle                & 1.526                                                   & 1.417                                                      & 1.527                                                      \\ \hline
MQ Score                & -0.0001                                                   & -0.043                                                      & 0.012                                                      \\ \hline
Same Issue Area         & 0.826                                                   & 0.718                                                      & 0.822                                                      \\ \hline
Year Difference         & -0.017                                                   & -0.018                                                     & -0.015                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the timep period when William Rehnquist was chief justice.}
\label{bootMPLE_vinson}
\end{table}

>>>>

\begin{table}[]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -5.445                                                 & -5.514                                                     & -5.296                                                     \\ \hline
Instar(2)               & 0.033                                                   & 0.028                                                      & 0.040                                                      \\ \hline
Outstar(2)              & 0.015                                                   & -0.001                                                      & 0.016                                                      \\ \hline
Mutual                  & 4.717                                                   & 4.093                                                 & 5.422                                                      \\ \hline
Triangle                & 1.337                                                   & 1.251                                                      & 1.475                                                      \\ \hline
MQ Score                & -0.009                                                   & -0.035                                                      & 0.087                                                      \\ \hline
Same Issue Area         & 1.205                                                   & 1.064                                                      & 1.237                                                      \\ \hline
Year Difference         & -0.076                                                   & -0.101                                                     & -0.072                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the timep period when Fred M. Vinson was chief justice.}
\label{bootMPLE_vinson}
\end{table}

\begin{table}[]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -5.042                                                 & -5.107                                                     & -4.952                                                     \\ \hline
Instar(2)               & 0.028                                                   & 0.026                                                      & 0.033                                                      \\ \hline
Outstar(2)              & 0.018                                                   & 0.017                                                      & 0.022                                                      \\ \hline
Mutual                  & 3.158                                                   & 1.469                                                 & 3.508                                                      \\ \hline
Triangle                & 1.500                                                   & 1.391                                                      & 1.506                                                      \\ \hline
MQ Score                & -0.106                                                   & -0.142                                                      & -0.067                                                      \\ \hline
Same Issue Area         & 1.334                                                   & 1.274                                                      & 1.378                                                      \\ \hline
Year Difference         & -0.031                                                   & -0.040                                                     & -0.029                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the timep period when Earl Warren was chief justice.}
\label{bootMPLE_vinson}
\end{table}

\begin{table}[]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -3.961                                                 & -4.036                                                     & -3.911                                                     \\ \hline
Instar(2)               & 0.016                                                   & 0.014                                                      & 0.037                                                      \\ \hline
Outstar(2)              & 0.004                                                   & 0.003                                                      & 0.006                                                      \\ \hline
Mutual                  & 2.528                                                   & 1.193                                                 & 3.007                                                      \\ \hline
Triangle                & 1.372                                                   & 1.248                                                      & 1.341                                                      \\ \hline
MQ Score                & -0.084                                                   & -0.096                                                      & -0.054                                                      \\ \hline
Same Issue Area         & 0.957                                                   & 0.917                                                      & 0.995                                                      \\ \hline
Year Difference         & -0.017                                                   & -0.019                                                     & -0.015                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the timep period when Warren E. Burger was chief justice.}
\label{bootMPLE_vinson}
\end{table}

\begin{table}[]
\centering
\begin{tabular}{|
>{\columncolor[HTML]{C0C0C0}}l |l|l|l|}
\hline
{\color[HTML]{333333} } & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Estimate} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Lower Bound} & \cellcolor[HTML]{C0C0C0}{\color[HTML]{333333} Upper Bound} \\ \hline
Edges                   & -3.618                                                 & -3.666                                                     & -3.539                                                     \\ \hline
Instar(2)               & 0.015                                                   & 0.014                                                      & 0.016                                                      \\ \hline
Outstar(2)              & 0.001                                                   & -0.002                                                      & 0.004                                                      \\ \hline
Mutual                  & 9.667                                                   & 8.218                                                 & 11.253                                                      \\ \hline
Triangle                & 1.546                                                   & 1.433                                                      & 1.551                                                      \\ \hline
MQ Score                & -0.007                                                   & -0.023                                                      & 0.032                                                      \\ \hline
Same Issue Area         & 0.852                                                   & 0.751                                                      & 0.846                                                      \\ \hline
Year Difference         & -0.016                                                   & -0.018                                                     & -0.014                                                          \\ \hline
\end{tabular}
\caption{Bootstrappped MPLE Results for the timep period when William Rehnquist was chief justice.}
\label{bootMPLE_vinson}
\end{table}
